Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-06 related_work.tex
related work tweaks

Recently, several researchers have investigated job placement and routing algorithms on dragonfly networks. Bogdan et al.\ proposed a novel solution for mapping applications exhibiting nearest neighbor communication patterns~\cite{hoefler-hpdc14}. They found that optimizing for throughput and not workload completion time is often misleading and the notion of system balance cited as a dragonfly design parameter is not always directly applicable to all workloads.
%\TODO{very brief blurb of what they did or what they found}. 
Jain et al. conducted a comprehensive analysis of various job placement and routing policies with regard to network link throughput on dragonfly network~\cite{jain-sc14}. Their work is based on an analytical model and synthetic workload. Bhatele et al. used coarse-grain simulation to study the performance of synthetic workloads under the different task mapping and routing policies on two-level direct networks~\cite{bhatele-sc11}. Misbah et al.\ focused on  the modeling of large-scale dragonfly networks with parallel event driven simulation. The dragonfly network model for million-node configurations presented in their work strongly scales when going from 1,024 to 65,536 MPI tasks on IBM Blue Gene/P and IBM Blue Gene/Q systems~\cite{codes-dragonfly}. The dragonfly network used in this paper is from their work. 
%\TODO{mention Misbah's dragonfly work, for which our work is based on}.

Our work complements the literature in the following ways. First, our simulations are driven by real application traces intended to be representative of production-scale application patterns. Second, we holistically examine behavior at both the overall system level as well as the application level, though we do not consider communication-pattern specific application mappings as Bogdan et al.\ did. Third, with the CODES simulation toolkit and related network models~\cite{codes, codes-dragonfly},  
%\TODO{cite codes, Misbah's dragonfly work}, 
we are able to simulate and examine system and application behavior at a very fine grain, collecting data at the dragonfly link level with packet-level fidelity. We believe these differences allowed us to uncover the ``bullying'' behavior, which to our knowledge is unreported in the literature.

>>>>

Recently, several researchers have investigated job placement and routing algorithms on dragonfly networks. Bogdan et al.\ proposed a communication-matrix-based analytic modeling framework for mapping application workloads onto network topologies~\cite{hoefler-hpdc14}. They found that, in the context of dragonfly networks, optimizing for throughput and not workload completion time is often misleading and the notion of system balance cited as a dragonfly design parameter is not always directly applicable to all workloads.
%\TODO{very brief blurb of what they did or what they found}. 
Jain et al. conducted a comprehensive analysis of various job placement and routing policies with regard to network link throughput on dragonfly network~\cite{jain-sc14}. Their work is based on an analytical model and synthetic workload. Bhatele et al. used coarse-grain simulation to study the performance of synthetic workloads under the different task mapping and routing policies on two-level direct networks~\cite{bhatele-sc11}. Mubarak et al.\ focused on  the modeling of large-scale dragonfly networks with parallel event driven simulation. The dragonfly network model for million-node configurations presented in their work strongly scales when going from 1,024 to 65,536 MPI tasks on IBM Blue Gene/P and IBM Blue Gene/Q systems~\cite{codes-dragonfly}. The dragonfly model used in this paper is from their work. 
%\TODO{mention Misbah's dragonfly work, for which our work is based on}.

Our work complements the literature in the following ways. First, our simulations are driven by real application traces intended to be representative of production-scale application patterns. Second, we holistically examine behavior at both the overall system level as well as the application level, though we do not consider communication-pattern specific application mappings as Bogdan et al.\ did. Third, with the CODES simulation toolkit and related network models~\cite{codes, codes-dragonfly},  
%\TODO{cite codes, Misbah's dragonfly work}, 
we are able to simulate and examine system and application behavior at a very fine grain, collecting data at the dragonfly link level with packet-level fidelity. We believe these differences allowed us to uncover the ``bullying'' behavior, which to our knowledge is unreported in the literature. However, in a sense, Bogdan et al.'s work suggests these types of behaviors as possibilities deriving from the balance-first design rationale for the dragonfly.
